---
title: "Developing Data Products Assignment 4"
author: "Scott Harrison"
date: "December 18, 2016"
output:
  ioslides_presentation: default
  beamer_presentation: default
  slidy_presentation: default
always_allow_html: yes
---

```{r setup}
```

##Key US Interest Rate Correlations  

In US Financial Markets some rates are strongly related to each other.  In particular, it is said that the 30-Year Mortgage rate follows the 10-Year Treasury Bond rate.  

Also, the Federal Reserve Funds rate is a key driver of other rates as well.  In some contexts, it is assumed that all long term rates are a built of short term rates.  

The app included here is a simple app that shows these rates for the last forty years and gives the user to test the correlations over different years in the past.

##Data Source

All data is sourced form the St Louis Fred website using an API Built into the R Code.  The data series are listed below.  More info can be found at the St Louis Fred site can be found at https://fred.stlouisfed.org/

##Data Series Citations

Board of Governors of the Federal Reserve System (US), 10-Year Treasury Constant Maturity Rate [WGS10YR], retrieved from FRED, Federal Reserve Bank of St. Louis; https://fred.stlouisfed.org/series/WGS10YR, December 18, 2016  

Freddie Mac, 30-Year Fixed Rate Mortgage Average in the United States© [MORTGAGE30US], retrieved from FRED, Federal Reserve Bank of St. Louis; https://fred.stlouisfed.org/series/MORTGAGE30US, December 18, 2016  

Board of Governors of the Federal Reserve System (US), Effective Federal Funds Rate [FF], retrieved from FRED, Federal Reserve Bank of St. Louis; https://fred.stlouisfed.org/series/FF, December 18, 2016  

##API Pull

The API call to pull data from the St. Louis Fred is a url string that returns JSON data.  That can then be parsed into a data fraom using `library(jsonlite)`.

```{r include = TRUE, eval = FALSE}
api_key <- "xxxxx"
file_type <- "json"
series <- c("MORTGAGE30US", "WGS10YR", "FF")
observation_start <- "1975-01-01"
observation_end <- "2017-01-01"
url <- paste("https://api.stlouisfed.org/fred/series/observations?",
             "&series_id=", series[1], "&api_key=", api_key,
             "&file_type=", file_type,
             "&observation_start=", observation_start,
             "&observation_end=", observation_end,
             sep = "")
mort <- fromJSON(txt = url)
mort$observations$date <- as.Date(mort$observations$date, "%Y-%m-%d")
mort$observations$value <- as.numeric(mort$observations$value)
```

##Sample Output

After running this a sample of the output in a data frame is below.

```{r echo = FALSE, eval = TRUE}
library(jsonlite)

api_key <- "5c569dd027d503376b3429eb11921ca3"
file_type <- "json"
series <- c("MORTGAGE30US", "WGS10YR", "FF")
observation_start <- "1975-01-01"
observation_end <- "2017-01-01"
url <- paste("https://api.stlouisfed.org/fred/series/observations?",
             "&series_id=", series[1],
             "&api_key=", api_key,
             "&file_type=", file_type,
             "&observation_start=", observation_start,
             "&observation_end=", observation_end,
             sep = "")

mort <- fromJSON(txt = url)
mort$observations$date <- as.Date(mort$observations$date, "%Y-%m-%d")
mort$observations$value <- as.numeric(mort$observations$value)
head(mort$observations)
```

##Conclusion

Using this freely available data and shiny, a self-serve analysis tool is possible.  The app is located at  

https://ksharrison.shinyapps.io/DDP_Assignment4/  

Other rates are available and this is a quick way to combine economic data and R into a user friendly interface for users that may want to do statistical anlalysis on this data, but may not have the R expertise to do it.  Also, it just saves time downloading and processing as well.
